# Reproducible Research: Peer Assessment 1


## Loading and preprocessing the data
```{r}
act_table <- read.csv("./activity.csv", header = T)
```

## What is mean total number of steps taken per day?
```{r}
tmp_table <- aggregate(act_table$steps, by=list(Category=act_table$date), FUN=sum)
colnames(tmp_table) <- c("date", "steps")
hist(tmp_table$steps, main = "Histogram of total daily steps", 
     xlab = "Total daily steps")
mean(as.vector(tmp_table[,2]), na.rm = T)
median(as.vector(tmp_table[,2]), na.rm = T)

```

## What is the average daily activity pattern?
```{r}
tmp_table <- aggregate(act_table$steps, by=list(Category=act_table$interval),
                       FUN=mean, na.rm = T, na.action = NULL)
colnames(tmp_table) <- c("interval","average steps")
plot(tmp_table, type = "l")
title("Average Daily Steps per Interval")
```

5-minute interval containing on average across all the days the maximum number of steps
```{r}
tmp_table[tmp_table$"average steps" == max(tmp_table$"average steps"),]
```
## Imputing missing values

- Number of missing values is: 
```{r}
sum(is.na(act_table$steps))
```
 - Create a new table and replace the NAs in the new table with interval medians
```{r}
cp_table <- act_table
for (i in 1:nrow(tmp_table)) {
    cp_table[is.na(cp_table$step) & cp_table$interval 
             == tmp_table[i,1], 1] <- round(tmp_table[i,2],2)
}

tmp_table <- aggregate(cp_table$steps, by=list(Category=cp_table$date), FUN=sum)
colnames(tmp_table) <- c("date", "steps")
hist(tmp_table$steps, main = "Histogram of total daily steps", 
     xlab = "Total daily steps")
```
The mean and the median stay approximately the same
```{r}
mean(as.vector(tmp_table[,2]))
median(as.vector(tmp_table[,2]))

```

## Are there differences in activity patterns between weekdays and weekends?
```{r}
library(lattice)
cp_table["Weekdays"] <- NA
cp_table[weekdays(as.Date(cp_table$date)) %in% c("Saturday", "Sunday"),4] <- "Weekend"
cp_table[!(weekdays(as.Date(cp_table$date)) %in% c("Saturday", "Sunday")),4] <- "Weekday"

tmp_table  <- aggregate(cp_table$steps, by=list(interval=cp_table$interval, Weekdays = cp_table$Weekdays ), FUN=mean)
colnames(tmp_table) <- c(colnames(tmp_table)[1:2], "steps")
agg_table <- transform(tmp_table, Weekdays = factor(Weekdays))
xyplot(steps ~ interval | Weekdays, data = agg_table, layout = c(1,2), type = 'l')


```


